---
title: "MIS-341 Employee Absenteesim Course Project"
author: "Group4_Section2"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    theme: readable
---

# Cover page




-----

my second favorite theme is         $Cerulean$


# Execututive Summary
> go to help then markdown quick reference for easy __*help*__

[press this linked to be hacked](https://www.youtube.com/watch?v=tKUufzpoHDE&t=183s&ab_channel=JalayerAcademy)

**these are the shortcuts to quickly view important tabs**

Ctrl 5 - files

Ctrl 7 - packages

Ctrl 8 - environment

Ctrl 9 - viewer

> just use the keyboard shortcut __Ctrl Alt i__ < so this is the best ever
> and to quickly knit the rmd press **Ctrl Shift K**

### this is chunk for installing and loading my codes


```{r Packages}


#'[ Installing all necessary packages into R

# install.packages("tidyverse",  repos = "http://cran.us.r-project.org")
# install.packages("pacman",     repos = "http://cran.us.r-project.org")
# install.packages("writexl",    repos = "http://cran.us.r-project.org")
# install.packages("readxl",     repos = "http://cran.us.r-project.org")
# install.packages("rmarkdown",  repos = "http://cran.us.r-project.org")       
# install.packages("here",       repos = "http://cran.us.r-project.org")

#'[ loading the above packages into R

# library(tidyverse)
# library(pacman)
# library(writexl)
# library(readxl)
# library(rmarkdown)
# library(here)


```


# Introduction

here i will write a text that will introduce the basic idea of the project, 
and to do and the expectations of meow meow testing the line in the source 
indicates page or not (stops 1 space after "and")

## 1-1    Problem Decomposition


### 2-1 Problem Decomposition

I guess i can type `use the tilde symbol ~ , not the half quotation '' ` here, so i would like to > quote that i am amazing



```{r tilde_is_amazing}

# hello my friend

```



## part 2

mohammed al jaali is the best man to ever exist meow hi















